Formalization, Mechanization and Automation of \\ G\"{o}del's Proof of God's Existence

### 2013-10-31 Talks/FU-Berlin/talk-part-1.tex
Organize images

\begin{frame}{} \small
\vskip1em
\begin{minipage}{.56\textwidth} 
\colorbox{gray}{\includegraphics[width=\textwidth]{spiegel1}} 
\vskip1em
Germany \\
- Telepolis \& Heise \\
- Spiegel Online \\
- FAZ \\
- Die Welt \\
- Berliner Morgenpost \\
- Hamburger Abendpost \\
- \ldots \\
\end{minipage} \hfill
%
\begin{minipage}{.3\textwidth}
Austria \\
- Die Presse \\
- Wiener Zeitung \\
- ORF \\
- \ldots \\

@@

\begin{frame}{Introduction --- Quick answers to your most pressing questions!} \large
\colorbox{gray}{\includegraphics[width=\textwidth]{MacBookGrab}} 
\pause
\vfill
Are we in contact with Steve Jobs? \hfill No \\[2em]
Do you really need a MacBook to obtain the results? \hfill No \\[2em]
Is Apple sending us money? \hfill No \\
\, \hfill (but maybe they should)
\end{frame}

@@

\begin{frame}{Introduction}
\vskip1em
\emph{\huge Wohl eine jede Philosophie kreist um den ontologischen
  Gottesbeweis} \\[1.5em]
(Adorno, Th. W.: Negative Dialektik. Frankfurt a. M. 1966, p.378)
\vfill
\begin{center}
\fcolorbox{gray}{white}{
\begin{minipage}{.9\textwidth}
\ldots \hfill
\includegraphics[height=2cm]{buch3.jpg} \hfill
\includegraphics[height=2cm]{buch2.jpg} \hfill 
\includegraphics[height=2cm]{buch4.jpg} \hfill
\includegraphics[height=2cm]{buch5.jpg} \hfill
\includegraphics[height=2cm]{buch6.jpg} \hfill
\includegraphics[height=2cm]{buch1.jpg} \hfill
\ldots
\end{minipage}
}
\end{center}
\end{frame}

@@

\begin{frame}{Introduction} \Large
Different Interests in Ontological Arguments: \\[1em]
\begin{itemize}
\item \textcolor{blue}{Philosophical:} Boundaries of Metaphysics \& Epistemology
  \begin{itemize}
  \item We talk about a metaphysical concept (God), 
  \item but we want to draw
      a conclusion for the real world. \\[1em]
  \item Necessary Existence (NE): metaphysical NE vs. logical NE  vs. modal NE \\[2em]
  \end{itemize} 
\item \textcolor{blue}{Theistic:} Successful argument should convince atheists \\[2em]
\item \textcolor{red}{Our:} Can computers (theorem provers) be used \ldots
  \begin{itemize}
  \item \ldots to formalize the definitions, axioms and theorems?
  \item \ldots to verify the arguments step-by-step?
  \item \ldots to fully automate (sub-)arguments? \\[1em]
  \end{itemize}
  \textcolor{red}{\emph{``Computer-assisted Theoretical Philosophy''}}
\end{itemize}
\end{frame}

>>>>

\begin{frame}{} \small
\vskip1em
\begin{minipage}{.56\textwidth} 
\colorbox{gray}{\includegraphics[width=\textwidth]{Images/News/spiegel1}} 
\vskip1em
Germany \\
- Telepolis \& Heise \\
- Spiegel Online \\
- FAZ \\
- Die Welt \\
- Berliner Morgenpost \\
- Hamburger Abendpost \\
- \ldots \\
\end{minipage} \hfill
%
\begin{minipage}{.3\textwidth}
Austria \\
- Die Presse \\
- Wiener Zeitung \\
- ORF \\
- \ldots \\

@@

\begin{frame}{Introduction --- Quick answers to your most pressing questions!} \large
\colorbox{gray}{\includegraphics[width=\textwidth]{Images/News/MacBookGrab}} 
\pause
\vfill
Are we in contact with Steve Jobs? \hfill No \\[2em]
Do you really need a MacBook to obtain the results? \hfill No \\[2em]
Is Apple sending us money? \hfill No \\
\, \hfill (but maybe they should)
\end{frame}

@@

\begin{frame}{Introduction}
\vskip1em
\emph{\huge Wohl eine jede Philosophie kreist um den ontologischen
  Gottesbeweis} \\[1.5em]
(Adorno, Th. W.: Negative Dialektik. Frankfurt a. M. 1966, p.378)
\vfill
\begin{center}
\fcolorbox{gray}{white}{
\begin{minipage}{.9\textwidth}
\ldots \hfill
\includegraphics[height=2cm]{Images/Books/buch3.jpg} \hfill
\includegraphics[height=2cm]{Images/Books/buch2.jpg} \hfill 
\includegraphics[height=2cm]{Images/Books/buch4.jpg} \hfill
\includegraphics[height=2cm]{Images/Books/buch5.jpg} \hfill
\includegraphics[height=2cm]{Images/Books/buch6.jpg} \hfill
\includegraphics[height=2cm]{Images/Books/buch1.jpg} \hfill
\ldots
\end{minipage}
}
\end{center}
\end{frame}

@@

\begin{frame}{Introduction} \Large
Different Interests in Ontological Arguments: \\[1em]
\begin{itemize}
\item \textcolor{blue}{Philosophical:} Boundaries of Metaphysics \& Epistemology
  \begin{itemize}
  \item We talk about a metaphysical concept (God), 
  \item but we want to draw
      a conclusion for the real world. \\[1em]
  \item Necessary Existence (NE): metaphysical NE vs. logical NE  vs. modal NE \\[2em]
  \end{itemize} 
\item \textcolor{blue}{Theistic:} Successful argument should convince atheists \\[2em]
\item \textcolor{red}{Ours:} Can computers (theorem provers) be used \ldots
  \begin{itemize}
  \item \ldots to formalize the definitions, axioms and theorems?
  \item \ldots to verify the arguments step-by-step?
  \item \ldots to fully automate (sub-)arguments? \\[1em]
  \end{itemize}
  \textcolor{red}{\emph{``Computer-assisted Theoretical Philosophy''}}
\end{itemize}
\end{frame}

### 2013-10-31 Talks/FU-Berlin/talk-part-7.tex
Organize images

\begin{transitionframe}
\textbf{Part F:}

@@

\begin{frame}{Some Comments and Reactions}
\colorbox{gray}{\includegraphics[width=.8\textwidth]{Comment1}}\\[.7em]

\, \hfill \colorbox{gray}{\includegraphics[width=.7\textwidth]{Comment2}}\\[.7em]

\colorbox{gray}{\includegraphics[width=.8\textwidth]{Comment3}}\\[1em]

@@

\begin{frame}[plain]
\colorbox{black}{\includegraphics[width=\textwidth]{TUWien-GodComputerC}}
\end{frame}

>>>>

\begin{transitionframe}{Images/Transitions/TrifidNebula(Nasa)(PublicDomain).jpg}
\textbf{Part F:}

@@

\begin{frame}{Some Comments and Reactions}
\colorbox{gray}{\includegraphics[width=.8\textwidth]{Images/Comments/Comment1}}\\[.7em]

\, \hfill \colorbox{gray}{\includegraphics[width=.7\textwidth]{Images/Comments/Comment2}}\\[.7em]

\colorbox{gray}{\includegraphics[width=.8\textwidth]{Images/Comments/Comment3}}\\[1em]

@@

\begin{frame}[plain]
\colorbox{black}{\includegraphics[width=\textwidth]{Images/Transitions/GodComputerC}}
\end{frame}
